Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-25 main_paper.tex
Adds a Kernel assumption and modifies the definition of the baseline estimator in the main text. That was copied from the general RD file in the boot-rd-general repository.

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

>>>>

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %

Assumption~\ref{A3} specifies the properties of the kernel function assumed by CCT, which we will also use in this paper.
\begin{assumption}[Kernel]\label{A3}
  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
\end{assumption}

This allows for the vast majority kernel functions commonly used by practitioners. Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model. For simplicity, in the following discussion we use the same function for all steps of estimation.
Potentially different kernel functions could be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.

For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i})
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i}).
\end{align*}
where $ K_{h}(u)=\frac{1}{h}K\left( \frac{u}{h}\right)$ with $K(\cdot)$ a kernel function.

Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.
